---
title: "DataFest"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(broom)

games <- read_csv("data/games.csv")
rpe <- read_csv("data/rpe.csv")
wellness <- read_csv("data/wellness.csv")
```

<<<<<<< HEAD




=======
```{r}
rpe1 <- rpe %>%
  filter(PlayerID == 1) %>%
  mutate(standard_rpe = scale(RPE))

rpe2 <- rpe %>%
  filter(PlayerID == 2) %>%
  mutate(standard_rpe = scale(RPE))

rpe3 <- rpe %>%
  filter(PlayerID == 3) %>%
  mutate(standard_rpe = scale(RPE))

rpe4 <- rpe %>%
  filter(PlayerID == 4)%>%
  mutate(standard_rpe = scale(RPE))

rpe5 <- rpe %>%
  filter(PlayerID == 5)%>%
  mutate(standard_rpe = scale(RPE))

rpe6 <- rpe %>%
  filter(PlayerID == 6)%>%
  mutate(standard_rpe = scale(RPE))

rpe7 <- rpe %>%
  filter(PlayerID == 7)%>%
  mutate(standard_rpe = scale(RPE))

rpe8 <- rpe %>%
  filter(PlayerID == 8)%>%
  mutate(standard_rpe = scale(RPE))

rpe9 <- rpe %>%
  filter(PlayerID == 9)%>%
  mutate(standard_rpe = scale(RPE))

rpe10 <- rpe %>%
  filter(PlayerID == 10)%>%
  mutate(standard_rpe = scale(RPE))

rpe11 <- rpe %>%
  filter(PlayerID == 11)%>%
  mutate(standard_rpe = scale(RPE))

rpe12 <- rpe %>%
  filter(PlayerID == 12)%>%
  mutate(standard_rpe = scale(RPE))

rpe13 <- rpe %>%
  filter(PlayerID == 13)%>%
  mutate(standard_rpe = scale(RPE))

rpe14 <- rpe %>%
  filter(PlayerID == 14)%>%
  mutate(standard_rpe = scale(RPE))

rpe15 <- rpe %>%
  filter(PlayerID == 15)%>%
  mutate(standard_rpe = scale(RPE))

rpe16 <- rpe %>%
  filter(PlayerID == 16)%>%
  mutate(standard_rpe = scale(RPE))

standard_rpe <- rbind(rpe1,rpe2,rpe3,rpe4,rpe5,rpe6,rpe7,rpe8,rpe9,rpe10,rpe11,rpe12,rpe13,rpe14,rpe15,rpe16)

standard_rpe <- standard_rpe %>% 
  select("Date", "PlayerID", "SessionType", "SessionLoad", "DailyLoad", "AcuteLoad", "ChronicLoad", "standard_rpe")
```
>>>>>>> 35c98b980b0982ad87cc6b7415f73d9e7c4a16d4

```{r}
standard_rpe <- standard_rpe %>%
  mutate(SessionType = case_when(
    SessionType %in% c("Combat", "Conditioning", "Game", "Mobility/Recovery", "Skills", "Speed", "Strength") ~ 
      SessionType, TRUE ~ "Rest"
  ))

sample <- rpe %>%
  drop_na() %>%
  select("PlayerID", "Duration", "RPE", "SessionLoad", "DailyLoad", "AcuteLoad", "ChronicLoad", "AcuteChronicRatio", "ObjectiveRating", "FocusRating")

small_sample <- sample %>%
  head(20)
  #c(26, 36, 78, 96, 109, 198, 204, 345, 389, 469, 490, 501, 521, 567, 589, 601, 623, 639)

write.csv(small_sample, "small_sample.csv")
```

